Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-11-07 sports_analytics.Rmd
Working on the gambling section.

# Sports Betting
@LopezBaumerMatthews2018 uses betting market data to [describe paper]

@@

Lacey, N. J. (1990). An estimation of market efficiency in the NFL point spread betting market. Applied Economics 22 117{129. : Finds the market to be efficient, though they did find some profitable betting rules over the period of time between 1984 and 1986

@@

Paul, R. J. and Weinbach, A. P. (2014). Market efficiency and behavioral biases in the wnba betting market. International Journal of Financial Studies 2 193{202.: Over the period of 2007–2012, they find that the market is still hard to beat.

>>>>

# Sports betting 
While @lopez2018 uses betting market data to model team strengths, it does not directly address strategies for betting or inefficiencies in betting markets.  Work such as @lacey1990, @Boulier2006,

@@

@Lacey1990 : Finds the market to be efficient, though they did find some profitable betting rules over the period of time between 1984 and 1986

@@

@PaulWeinbach2014 Market efficiency and behavioral biases in the wnba betting market
